### 2022-05-26 Manuscript/S1 - Clavis schema.tex
Update after feedback

    "statements"

@@

      "description": "Short description of the key (valid markdown).",

@@

      "description": "Hyperlink to the source of the key (valid url).",

@@

      "description": "The region for which the key is valid (e.g. covers
all subtaxa), represented as a geography object.",

@@

      "description": "The moment the key was made or first published, as

@@

      "description": "The url of where the key lives (to check for newer
versions).",

@@

      "description": "Taxa (e.g. species) the key can resolve to. Do not
have to be exclusively taxonomic units.",

@@

      "description": "Persons that are connected to (parts of) the key,
such as creators.",

@@

      "description": "Organizations that are connected to (parts of) the
key or persons, such as employers and publishers.",

@@

media elements, corresponding to the languages supported by the key.",

@@

      "description": "String used as an internal ID for an organization.

@@

      "description": "String used as an internal ID for a media element.

@@

              "pattern": "^data:([a-z0-9/]+);base64,([a-zA-Z0-9+/=]+)$"

@@

          "description": "The number of pixels horizontally (if a bitmap

@@

      "description": "A media element (collection of various formats of
the same media object).",

@@

      "description": "Service used by the key, for media files, taxonomy
and/or nomenclature, species distributions, etc.",

@@

          "description": "Media or illustration that informs the user on
the requirements to the user.",

@@

          "description": "Name that can be shown while fetching the name
externally. Also useful for editing the key.",

@@

          "description": "Whether the key should stop when this taxon is
the only remaining possibility, even when it has multiple children

@@

          "description": "Reference to a taxon at one or more providers,
each as an object with a provider id and a taxon id at that provider.",

@@

@@

          "description": "The media element(s) of the character. Can be
used to inform user of relevant structures etc.",

@@

true (either answered or all alternatives ruled out). Can use !, &&, ||,
(, ), <, >, =.",

@@

@@

          "description": "Media element(s) that illustrate the state.",

@@

          "description": "Lowest numerical value of the state (over all
taxa).",
          "comment": "Only to be used for numerical characters",
          "description": "Highest possible numerical value of the state
(over all taxa).",
          "comment": "Only to be used for numerical characters",
          "description": "Step size of the state (steps between min and
max, over all taxa).",
          "comment": "Only to be used for numerical characters",
          "description": "Unit in which the state is measured or
counted.",
          "comment": "Only to be used for numerical characters. Accepts
object for multilingual support.",

@@

      "description": "A fact connecting a taxon and a character through
a certain value.",

@@

Must be either the id of a state, or an array of floats [min, max] for a
numerical range.",

@@

          "description": "Extended description of the taxon having this
property that supplements the description (valid markdown).",

>>>>

    "statements",
    "persons"

@@

      "description": "Short description of the key (valid

@@

      "description": "Hyperlink to the source of the key (valid

@@

      "description": "The region for which the key is valid (e.g.
covers all subtaxa), represented as a geography object.",

@@

      "description": "The moment the key was made or first published,
as 'YYYY-MM-DD hh:mm:ss'.",

@@

      "description": "The url of where the key lives (to check for
newer versions).",

@@

      "description": "Taxa (e.g. species) the key can resolve to. Do
not have to be exclusively taxonomic units.",

@@

      "description": "Persons that are connected to (parts of) the
key, such as creators.",

@@

      "description": "Organizations that are connected to (parts of)
the key or persons, such as employers and publishers.",

@@

media elements, corresponding to the languages supported by the

@@

      "description": "String used as an internal ID for an
organization. Lowercase alphanumeric and underscores are allowed.",

@@

      "description": "String used as an internal ID for a media
element. Lowercase alphanumeric and underscores are allowed.",

@@

              "pattern":
"^data:([a-z0-9/]+);base64,([a-zA-Z0-9+/=]+)$"

@@

          "description": "The number of pixels horizontally (if a
bitmap image or video).",

@@

      "description": "A media element (collection of various formats
of the same media object).",

@@

      "description": "Service used by the key, for media files,
taxonomy and/or nomenclature, species distributions, etc.",

@@

          "description": "Media or illustration that informs the user
on the requirements to the user.",

@@

          "description": "Name that can be shown while fetching the
name externally. Also useful for editing the key.",

@@

          "description": "Whether the key should stop when this taxon
is the only remaining possibility, even when it has multiple children

@@

          "description": "Reference to a taxon at one or more
providers, each as an object with a provider id and a taxon id at that
provider.",

@@

            "type",

@@

          "description": "The media element(s) of the character. Can
be used to inform user of relevant structures etc.",

@@

true (either answered or all alternatives ruled out). Can use !, &&,
||, (, ), <, >, =.",

@@

          "description": "The minimum numerical value for the
character."
          "description": "The maximum numerical value for the
character."
          "description": "The increments with which the numerical
value of the character can be specified."
          "description": "The unit of the numerical value.",

@@

          "description": "Media element(s) that illustrate the
state.",

@@

@@

      "description": "A fact connecting a taxon and a character
through a certain value.",

@@

Must be either the id of a state, or an array of floats [min, max] for
a numerical range.",

@@

          "description": "Extended description of the taxon having
this property that supplements the description (valid markdown).",
